Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2021-09-27 doc/main_jfm.tex
yny tex
update table
corrected table
final language/figure edit; b coeffs need double checking

\begin{abstract}
  We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
  In this work, we study the dynamics of many-body systems immersed in a
  viscous fluid with a specified interparticle force. In particular, we
  apply a hydrophobic attraction potential (HAP) using a Janus type
  granular system to model lipid bilayer membranes. Coupling with an
  efficient integral equation method for rigid bodies in Stokes flow and
  a previous developed HAP solver, the deformations of a two-dimensional
  vesicle such as tank-treading motion and membrane ruptures can be
  observed under different values of the shear rate. Moreover, an
  efficient integral equation method is adopted for solving the screened
  Laplace equation and the mobility problem where it can accurately
  calculate hydrophobic and hydrodynamic interactions between near
  touched boundaries.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the
Janus particle (often a spherical particle with a hydrophobic and a
hydrophilic hemisphere) exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering.
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles in a viscous solvent is inevitably the combination of long-range
hydrodynamics interactions with both short- and intermediate-range 
particle-particle interactions. Such multi-scale nature of Janus particle dynamics underlies 
the richness of a Janus particle suspension, as \cite{deGennes1991} suggested by the example of 
a ``thin film of Janus grains" that can breathe due to the interstices between Janus particles.

Recently~\cite{Fu20}
illustrated that the hydrophobic interactions between Janus particles in
a viscous solvent can be used as a coarse-grained model to capture the
mechanics of an elastic bilayer membrane of amphiphilic macromolecules
such as lipids. Depending on the total number of Janus particles and
their geometry, in a viscous solvent, Janus particles can aggregate to
form a micelle, a patch of bilayer membrane with open ends, and a
self-enclosed bilayer membrane (referred to as a JP vesicle). Using a
hybrid continuum model for the interactions between amphiphilic
particles in a viscous solvent and with a boundary integral
formulation,~\cite{Fu20} showed that the membrane granularity during
fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

In molecular dynamics (MD) simulations, the lipid bilayer membranes are
often approximated by an implicit solvent coarse-grained model for
lipids (as in the Martini code), where their hydrodynamic interactions
are simplified by an implicit solvent. The long-range hydrodynamic
interactions and the induced long-range lipid interactions can be
captured by combining the Dry Martini with a lattice Boltzmann MD.
\cite{Brandner2019} used this methodology to simulate the hydrodynamics
of a nano-sized vesicle under a shear flow, and reproduced the well-know
vesicle hydrodynamics such as tank-treading, tumbling, and inter-leaflet
slippage (reported from simulations of the Helfrich-type continuum
model).

In this work we extend the hybrid continuum model in~\cite{Fu20} for the
Janus suspension to incorporate the collective hydrodynamics of a Janus
suspension under various flows: a linear shear flow, an elongation flow,
and a Poiseuille flow. We demonstrate that a JP vesicle behaves like
a vesicle in these flowing conditions. In particular, we show that a
JP vesicle undergoes tank-treading in a shear flow and vertical
migration in a Poiseuille flow. Furthermore we use the hybrid continuum
model to investigate the inter-leaflet slippage and rupture of a bilayer
membrane due to an imposed flow. Finally, we compare a pair of
interacting JP vesicles with a continuum model of a pair of vesicles.

We require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but potentially expensive nonlinear
complementarity problems must be solved at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively weak non-stiff repulsive
force.

This paper is organized as follows. In \S~\ref{sec:governing_eqs} we
present the formulation for the Janus particles in a viscous fluid in
the zero-Reynolds number regime. In \S~\ref{sec:IEM} we extend the
hybrid continuum model for a Janus suspension to include the effects of
a far-field flow via the mobility problem formulation. In
\S~\ref{results} we validate our model and present simulation results
for a single and pair of JP vesicles under various flowing conditions.
Finally we provide discussion and outlook for future directions in
\S~\ref{conclusion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution
  $u$ of \eqref{eq:SL}. Red is for $u = 1$ and blue is for $u = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve, $A$ is the enclosed area, and $L$ is the arc
  length. Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tank-Treading Vesicles}
\begin{figure}
\begin{center}
\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
%\hspace{-0.6cm}
%\includegraphics[height=2in]{ReducedArea.pdf}
%\hspace{0.6cm}
%\includegraphics[height=2in]{DecayRate.eps}\\
%\includegraphics[height=2in]{ArcLength.pdf}
%\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4}
 JP vesicles loose enclosed area and conserve length in shear flow. 
  Panel (a) gives the reduced area over time
  for four different shear rates. The smooth curves are a best-fit
  exponential curve. There is commensurate increase in excess length (panel (b)), 
  but the arc length of the mid plane curve is more or less constant.   
   The legend in panel (b) applies to panels (a)--(c).
  Panel (d) plots the steady-state reduced area and the decay rate $k$ (inset) using the exponential fit
  to the data in panel (a). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
Our simulation studies begin by showing, for the first time, that a JP suspension with hydrophobic attraction 
behaves as a tank-treading vesicle
%with zero viscosity contrast between the fluids inside and
%outside of the vesicle
(\cite{Finken08, Shaqfeh11}).
The centroid of the baseline $58$-body JP vesicle lies at the origin 
and the background shear flow 
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
\end{align} 
is applied for
shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
and $\mathbf{e}_y$ for the horizontal and vertical directions, respectively.
We use the dimensionless shear rate $\chi = \dot \gamma$ ns.

\begin{figure}
\begin{center}
\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
\includegraphics[width=11cm]{Figure5B_Wrapper.pdf}
%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
%\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} 
  There is inter-monolayer slip present in the JP vesicle tank-treading motion at all shear rates.  
  Panel (a) tracks the angle  $\theta(t)$ between a pair of particles (blue and yellow) with respect to
  the JP vesicle centroid. The shear rate is $\chi=0.005$ and in the right figure, the yellow particle
  will complete two and a quarter revolutions in the same time the blue particle completes two revolutions.
  The curves in panel (b) are the mean change in angle for various shear rates. 
  Slip velocity generally increases with shear rate but 
  we have marked two outliers (times symbols). }
\end{figure}

Figure~\ref{figure3} shows snapshots of the JP vesicle in the
shear flow with $\chi=0.0025$. 
Under the background flow, the rigid-body boundary condition \eqref{eq:rigid_bc} causes the 
particle suspension to stretch apart. This perturbation  
disrupts the preferred particle orientations and exposes the hydrophobic core to bulk water (Figure~\ref{figure3}, red region).
In response, hydrophobic attraction \eqref{eq:hydrophobicAttraction} causes the 
particles to reorient and form a  somewhat elliptically-shaped suspension.  
Panels (a) shows the initial configuration and panel (b) shows the later, fully-formed, clockwise tank-treading motion. 
The JP suspension maintains its bilayer structure throughout the simulation. 
%

To extract physical quantities, 
let $A^* = 4\pi A/L^2$ be the reduced area and $\Delta=L/\sqrt{A^*/\pi}-2\pi$ the excess length of the bilayer
structure (\cite{Finken08}).
Here, $A$ is the enclosed area and $L$ is the total length of the JP vesicle  (Figure \ref{fig:figure0}a).
Figure~\ref{figure4} shows the evolution of the same for various shear rates.
Panels (a) and (b) show that $A^*$ decreases and $\Delta$ increases with time, respectively,
and that the rate of decrease/increase grows with shear rate. 
The total arc length, however, remains constant for all time
for all four shear rates (panel (c)).
We conclude that the JP vesicle loses area and that the bilayer behaves as a permeable membrane. 
Due to granularity, the tank-treading motion has some wobble and this is the source
of the oscillations in the panels of Figure~\ref{figure4}.

Since the starting configuration is nearly circular, the reduced area
decreases from an initial value close to $1$ and tends to a steady-state value $A^*_{\infty}$. 
The curves in panel (a) are fit of the exponential model $A^* = A^*_{\infty} + (1-A^*_{\infty}) \exp(-kt)$.
Panel (d) shows that $A^*_{\infty}$ decreases with shear rate, 
and that reduced area converges to a steady state earlier when the shear rate is lower (inset).

We point out that the range of values for $\chi$ where we measured for tank-treading 
correspond to shear rates $\dot \gamma = O(10^6$ s$^{-1}$) 
which gives fluid velocities like m s$^{-1}$ in the vicinity of the  vesicle.  
While seemingly large, these values are consistent with prior MD studies (\cite{Brandner2019})
and are a consequence of the fact that the magnitude of elastic membrane stresses grows inversely 
with the vesicle radius; larger shear rates are required to produce the viscous stresses needed to 
appreciably deform smaller vesicles.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Inter-Monolayer Friction}
We observe inter-monolayer slip in the tank-treading, JP vesicle at all shear rates. 
The two leaflets of the vesicle are not bound together, but rather are able to slide 
past one another. This sliding is limited by viscous friction of the aqueous gaps between particles
and by the constant unbinding and binding of particles pairs in apposing leaflets.  
The phenomenon is consistent with prior MD results (\cite{Zgorski2019, denOtter2007}).

Figure~\ref{figure5}a illustrates the process by tracking the angle $\theta(t)$
between two particles, one blue and the other yellow, relative to the vesicle centroid. 
It is clear from the growth in angle that the outer leaflet has a tangential velocity that is larger  
then that of the inner leaflet.  
Figure~\ref{figure5}b plots the mean, particle-pair angle for various shear rates. 
It suggests that the inter-monolayer slip velocity generally increases with shear rate.

From the data, we are able to define an inter-monolayer friction coefficient  
\begin{align}
  b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle},
\end{align}
where $F$ is the tangential force jump, $L$ is the length of the midplane $C_M$ (Figure~\ref{figure5}a), $U$ is the slip velocity, and 
$\langle \cdot \rangle$ denotes the time average. 
To measure inter-monolayer slip $U$, we compute the mean tangential velocity of the particles in the outer monolayer
and subtract from it the mean tangential velocity of the particles in the inner monolayer. 
To calculate the tangential force jump $F$, we let 
\begin{equation}
F_h = \int_{\mathcal{C}_M^+} 
    \ttau \cdot \sigma \cdot \nnu \,\dif s -  \int_{\mathcal{C}_M^-} 
    \ttau \cdot \sigma \cdot \nnu \,\dif s 
\end{equation}
where $C_M^+$ and $C_M^-$ are target curves obtained by moving the midplane curve $C_M$ (Figure~\ref{figure5}a)
a distance $h$ along the outward, respectively inward, unit normal.  Actually, we calculate $F_h$ for several values of $h$ 
and then define $F$ to by extrapolating to zero distance giving a jump in tangential shear force across the midplane.

\begin{table}
\caption{Friction Coefficients}
\centering
\begin{tabular}{c c c c c c c c }
 $\chi$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
\hline                    
$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
%$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
%$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87*  & 0.22 &0.21 & 1.29* & 0.31 & 0.30\\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}

Table~\ref{table1} provides dimensional friction coefficients $b$ for
several shear rates. The coefficients generally lie within the
range 0.2 to 0.3 pN ns nm$^{-3}$ which is in good quantitative agreement with
values previously reported in the literature (\cite{sch-vla-mik2010}
and~\cite{denOtter2007}).  
The data contain two outliers (Table~\ref{table1}, * symbol).
These correspond to the two outliers in the slip velocities (Figure~\ref{figure5}b, times symbol). 
We suspect that due to the finite particle size, the granular wobble of the tank-treading motion is more prominent for some
shear rates, causing some slip velocities to be lower than expected.

@@

In \cite{Fu20} a mathematical model is developed to quantify the macroscopic assembly and mechanics of 
a JP bilayer in a viscous solvent. The interactions between JPs are formulated as a second-kind integral equation, which is coupled to the incompressible Stokes equations for the surrounding incompressible fluid at the zero-Reynolds-number limit.  Numerical simulations of a JP suspension reveal self-assembly of JPs into micelles and bilayers, and also provide an alternative means for computing the mechanical moduli of a JP membrane, which often requires the knowledge of an equation of state from experiments on a colloidal membrane~(\cite{Balchunas2019_SM}).
In this study we used this integral formulation and numerical algorithm to simulate the hydrodynamics of JP vesicles. 
%
%This study presents a coarse-grained model for JP vesicles that focuses
%on the hydrophobic interactions between coarse-grained lipids and
%hydrodynamic interactions. In contrast to molecular dynamic simulations,
%the hydrophobic interactions exhibit the self-assembly property of the
%lipid bilayer membrane. The proposed energy potential combined with the
%mobility problem for rigid body motions captures membrane mechanics
%including deformations, stretching modulus, and permeability of a JP
%membrane. 
%
Results in this work show great potential to study Janus colloids~(\cite{Bradley2017,Mallory2017}) and the morphology of colloid
surfactants~(\cite{Bradley2016}). 
%
%This work is highly applicable with fields in material science
%and condensed matter physics such as Janus
%colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
%match experimental results such as the morphology of colloid
%surfactants~(\cite{Bradley2016}). 
%%
For example, with the flexibility of the model, we can specify the boundary condition on JP surfaces based on the chemicals used in experiments. 
%This can be an assist to study of interparticle interactions and chemical compositions in industry.

>>>>

\begin{abstract}
  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic particles suspended in a viscous background flow. 
  The interparticle force comes from a specific hydrophobic attraction potential (HAP)
  that has been shown to model lipid bilayer membranes. 
  We adopt an   efficient integral equation method for solving the screened
  Laplace equation and the mobility problem where it can accurately
  calculate hydrophobic and hydrodynamic interactions between near
  touched boundaries.    Under a linear shear flow,  we observe the tank-treading deformation
  in a two-dimensional  vesicle for various values of the shear rate.
  The results yield measurements 
  of inter-monolayer friction and membrane permeability. Large shear rates lead to membrane rupture. 
  The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
  interactions in shear and extensional flows.
%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
%  In this work, we study the dynamics of many-body systems immersed in a
%  viscous fluid with a specified interparticle force. In particular, we
%  apply a hydrophobic attraction potential (HAP) using a Janus type
%  granular system to model lipid bilayer membranes. Coupling with an
%  efficient integral equation method for rigid bodies in Stokes flow and
%  a previous developed HAP solver, the deformations of a two-dimensional
%  vesicle such as tank-treading motion and membrane ruptures can be
%  observed under different values of the shear rate. Moreover, an
%  efficient integral equation method is adopted for solving the screened
%  Laplace equation and the mobility problem where it can accurately
%  calculate hydrophobic and hydrodynamic interactions between near
%  touched boundaries.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{intro}Introduction}
Described by physicist Pierre-Gilles de Gennes as ``another animal in soft matter physics", the
Janus particle--often a spherical particle with a hydrophobic and a
hydrophilic hemisphere--exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering (\cite{deGennes1991}).
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles in a viscous solvent is inevitably the combination of long-range
hydrodynamics interactions with both short- and intermediate-range 
particle-particle interactions. Such multi-scale nature of Janus particle dynamics underlies 
the richness of a Janus particle suspension, as \cite{deGennes1991} suggested by the example of 
a ``thin film of Janus grains" that can breathe due to the interstices between Janus particles.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution
  $u$ of \eqref{eq:SL}. Red is for $u = 1$ and blue is for $u = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve, $A$ is the enclosed area, and $L$ is the arc
  length. Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

Recently,~\cite{Fu20}
illustrated that the hydrophobic interactions between Janus particles (JP) in
a viscous solvent can be used as a coarse-grained model to capture the
mechanics of an elastic bilayer membrane of amphiphilic macromolecules
such as lipids. Depending on their total number and
geometry, JP suspensions can aggregate to
form a micelle, a patch of bilayer membrane with open ends, and a
self-enclosed bilayer membrane, referred to as a JP vesicle. Using a
hybrid continuum model for the interactions between amphiphilic
particles in a viscous solvent and with a boundary integral
formulation,~\cite{Fu20} showed that the granularity of membrane remodeling, 
as occurs during fusion and fission of bilayers,
can be accurately captured by the coarse-grained model.  
%This boundary integral formulation has inspired more recent work

In the present work, we extend the hybrid continuum model in~\cite{Fu20} for the
Janus suspension to incorporate the collective hydrodynamics of a Janus
suspension under various flows. The JP vesicles in our simulations replicate  
well-know vesicle hydrodynamics such as tank-treading and inter-leaflet
slippage in a shear flow and migration in Poiseuille flow from continuum models. Furthermore we use the hybrid continuum
model to investigate permeability and rupture of a bilayer
membrane due to an imposed flow. 
Finally, we compare a pair of
interacting JP vesicles with a continuum model of a pair of vesicles.

\cite{Brandner2019} used the coarse-grained force field with a lattice Boltzmann molecular dynamics to simulate the hydrodynamics
of a nano-sized vesicle under a shear flow.  
In MD simulations, the hydrodynamic interactions 
for the solvent phase are often approximated by an implicit solvent coarse-grained model.
In the present work, the hydrodynamic interactions come from the mobility problem
for the Stokes equations for the incompressible, viscous solvent.

We require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but do require solving potentially expensive nonlinear
complementarity problems at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively weak non-stiff repulsive
force.

The paper is organized as follows.  In \S~\ref{sec:governing_eqs} we
present the formulation for the Janus particles in a viscous fluid in
the zero-Reynolds number regime (Figure \ref{fig:figure0}a). 
In \S~\ref{sec:IEM} we extend the
hybrid continuum model for a Janus suspension to include the effects of
a far-field flow via the mobility problem formulation. In
\S~\ref{results} we validate our model and present simulation results
for a single JP vesicle (Figure \ref{fig:figure0}d) and for a pair of JP vesicles (Figure \ref{fig:figure0}e) 
under various flowing conditions.
Finally we provide discussion and outlook for future directions in
\S~\ref{conclusion}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tank-Treading Vesicles}
\begin{figure}
\begin{center}
\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
%\hspace{-0.6cm}
%\includegraphics[height=2in]{ReducedArea.pdf}
%\hspace{0.6cm}
%\includegraphics[height=2in]{DecayRate.eps}\\
%\includegraphics[height=2in]{ArcLength.pdf}
%\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4}
 JP vesicles lose enclosed area but conserve length in shear flow. 
  Panel (a) gives the reduced area over time
  for four different shear rates. The monotonic curves are a 
  two-exponential best fit. There is a commensurate increase in excess length (panel (b)), 
  but the arc length of the mid plane curve is more or less constant for all shear rates  (panel (c)).
  The inset in panel (c) is for shear rate 0.003. The legend in panel (b) applies to panels (a)--(c).
  Panel (d) plots the steady-state reduced area and the decay rate $k_2$ (inset) coming from the fitting
  data in panel (a). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
Our simulation studies begin by showing, for the first time, that a JP suspension with hydrophobic attraction 
behaves as a tank-treading vesicle
%with zero viscosity contrast between the fluids inside and
%outside of the vesicle
(\cite{Finken08, Shaqfeh11}).
The centroid of the baseline, $58$-body JP vesicle lies at the origin 
and the background shear flow 
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
\end{align} 
is applied for
shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
and $\mathbf{e}_y$ for the horizontal and vertical directions, respectively.
We use the dimensionless shear rate $\chi = \dot \gamma$ (s$^{-1}$) ns.

\begin{figure}
\begin{center}
\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
\includegraphics[width=11cm]{Figure5B_Wrapper.pdf}
%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
%\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} 
  There is inter-monolayer slip present in the JP vesicle tank-treading motion at all shear rates.  
  Panel (a) tracks a pair of particles (blue and yellow). 
  The shear rate is $\chi=0.005$ and in the right figure, the yellow particle
  will complete two and a quarter revolutions in the same time the blue particle completes two revolutions.
  The curves in panel (b) are the distance the outer leaflet has slid past the inner leaflet. 
  The slopes of the curves gives the slip velocity. 
  With the exception of $\chi = 0.0035$, slip velocity is generally monotonic in the shear rate. }
\end{figure}

Figure~\ref{figure3} shows snapshots of the JP vesicle in the
shear flow with $\chi=0.0025$. 
Under the background flow, the rigid-body boundary condition \eqref{eq:rigid_bc} causes the 
particle suspension to elongate. This perturbation  
disrupts the preferred particle orientations and exposes the hydrophobic core to bulk water (Figure~\ref{figure3}, red region).
In response, hydrophobic attraction \eqref{eq:hydrophobicAttraction} causes the 
particles to reorient and form a  somewhat elliptically-shaped suspension.  
Panels (a) shows the initial configuration and panel (b) shows the later, fully-formed, clockwise tank-treading motion. 
The JP suspension maintains its bilayer structure throughout the simulation. 
%

To extract physical quantities, 
let $A^* = 4\pi A/L^2$ be the reduced area and $\Delta=L/\sqrt{A/\pi}-2\pi$ the excess length of the bilayer
structure (\cite{Finken08}).
Here, $A$ is the enclosed area and $L$ is the total length of the JP vesicle  (Figure \ref{fig:figure0}a).
Figure~\ref{figure4} shows the evolution of the same for various shear rates.
Panels (a) and (b) show that $A^*$ decreases and $\Delta$ increases with time, respectively,
and that the rate of decrease/increase grows with shear rate. 
The total arc length, however, remains constant for all time
for all four shear rates (panel (c)).
We conclude that the JP vesicle loses area and that the bilayer behaves as a permeable membrane.

Since the starting configuration is nearly circular, the reduced area
decreases from an initial value close to $1$ and tends to a steady-state value $A^*_{\infty}$. 
The data in panel (a) are fit by the model 
$A^* = (A^*_{\infty}-a_1-a_2) + a_1 \exp(-k_1t) + a_2 \exp(-k_2t),$ $0 < k_2 < k_1$.
Panel (d) shows that $A^*_{\infty}$ decreases with shear rate. 
The JP vesicle achieves a steady-state reduced area 
earlier when the shear rate is low (inset), but the decay rate $k_2$ is more or less constant for higher shearer rates.

The oscillations in the data of Figure~\ref{figure4} are due to the
granularity of the JP vesicle. 
The inset of Figure~\ref{figure4}c zooms in on the arc length data for the shear rate $\chi = 0.003$.
It shows that the oscillations are smooth and well-resolved by our second-order Adams-Bashforth scheme.

We point out that the range of values for $\chi$ where we measured for tank-treading 
correspond to shear rates $\dot \gamma = O(10^6$ s$^{-1}$) 
which gives fluid velocities O(m s$^{-1}$) in the vicinity of the  vesicle.  
While large, these values are identical to ones used in prior MD studies (\cite{Brandner2019})
and are a consequence of the fact that larger shear rates are required to produce the viscous stresses needed to 
appreciably deform smaller vesicles.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Inter-Monolayer Friction}
We observe inter-monolayer slip in the tank-treading, JP vesicle at all shear rates. 
Since they are not bound, the two leaflets of the vesicle are able to slide 
past one another. This sliding is limited by viscous friction of the aqueous gaps between particles
and by the constant unbinding and binding of particles pairs in apposing leaflets.  
The phenomenon is consistent with prior MD results (\cite{Zgorski2019, denOtter2007}).

Figure~\ref{figure5}a illustrates the process by tracking the distances traveled 
by a pair of particles. 
In the left image, the blue and yellow particle lie next to each other. 
In the right-most panel, the yellow particle has traveled further than the blue particle. 
This suggests that the tangential velocity of the outer leaflet is larger than that of the inner leaflet.
The difference in their velocities is the slip velocity $U(t)$  and $s(t) = \int_0^t dU $ records the distance
one leaflet has slid past the other.

Figure~\ref{figure5}b plots the sliding distance for various shear rates. 
From the data, we define an inter-monolayer friction coefficient  
\begin{align}
  b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle},
\end{align}
where $F$ is the tangential force jump, $L$ is the length of the midplane $C_M$ (Figure~\ref{figure5}a), $U$ is the slip velocity, and 
$\langle \cdot \rangle$ denotes the time average. 
We define the tangential force jump $F$ to be the tangential shear force on the outer leaflet minus the tangential shear force on the inner leaflet. 
However, it does not make sense to integrate along a curve passing through the particles.  
To calculate the tangential force jump $F$, we instead let 
\begin{equation}
F_h = \int_{\mathcal{C}_M^+} 
    \ttau \cdot \sigma \cdot \nnu \,\dif s -  \int_{\mathcal{C}_M^-} 
    \ttau \cdot \sigma \cdot \nnu \,\dif s 
\end{equation}
where $C_M^+$ and $C_M^-$ are target curves obtained by moving the midplane curve $C_M$ (Figure~\ref{figure5}a)
a distance $h$  outward, respectively inward, along the unit normal.  
We sample $F_h$ for $h = \pm 1.5, \pm 2.5, \pm 3.5$ times the particle radius 
and define $F$ by extrapolating to zero distance.

\begin{table}
\caption{Friction Coefficients}
\centering
\begin{tabular}{c c c c c c c c }
 $\dot\gamma$  (ns$^{-1}$) & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
\hline                    
%$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
%$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
%$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
%$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87*  & 0.22 &0.21 & 1.29* & 0.31 & 0.30\\ 
$b$ (pN$\cdot$ns nm$^{-3}$)    & 1.01 & 3.40 &   3.70  &   5.01 &   5.38  &   5.75  &   6.25 \\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}

Table~\ref{table1} provides dimensional friction coefficients $b$ for
several shear rates. The coefficients generally lie within the
range 1 to 6 pN ns nm$^{-3}$ which is in good quantitative agreement with
values previously reported in the literature (\cite{sch-vla-mik2010}
and~\cite{denOtter2007}).  \cite{denOtter2007} give  
$b = 2.4 \times 10^6$ Pa m$^{-1}$ s = 
2.4 pN nm$^{-3}$ ns from their MD study, for example.

@@

\cite{Fu20} developed a mathematical model to quantify the macroscopic assembly and mechanics of 
a JP bilayer in a viscous solvent. 
The interactions between JP are formulated as a second-kind integral equation, 
which is coupled to the Stokes equations for the surrounding incompressible fluid 
at the zero-Reynolds-number limit.  
Numerical simulations of a JP suspensions revealed self-assembly of JP into micelles 
and bilayers, providing an alternative means for computing mechanical moduli, 
which often requires the knowledge of an equation of state from experiments on a colloidal membrane~(\cite{Balchunas2019_SM}).
%
%This study presents a coarse-grained model for JP vesicles that focuses
%on the hydrophobic interactions between coarse-grained lipids and
%hydrodynamic interactions. In contrast to molecular dynamic simulations,
%the hydrophobic interactions exhibit the self-assembly property of the
%lipid bilayer membrane. The proposed energy potential combined with the
%mobility problem for rigid body motions captures membrane mechanics
%including deformations, stretching modulus, and permeability of a JP
%membrane. 
%
Results in this work show great potential to study Janus colloids~(\cite{Bradley2017,Mallory2017}) and the morphology of colloid
surfactants~(\cite{Bradley2016}). 
%
%This work is highly applicable with fields in material science
%and condensed matter physics such as Janus
%colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
%match experimental results such as the morphology of colloid
%surfactants~(\cite{Bradley2016}). 
%%
For example, with the flexibility of the model, we can specify the boundary condition on JP surfaces based on the chemicals used in experiments. 
%This can be an assist to study of interparticle interactions and chemical compositions in industry.
